# Reproducible Research: Peer Assessment 1
 ```{r setoptions,echo=TRUE}
  opts_chunk$set(echo=TRUE)
 ```

## Loading and preprocessing the data
 ```{r loaddata}
  file<-read.csv("activity.csv", colClasses = c("numeric", "Date", "numeric"))
 head(file)
 ```
## What is mean total number of steps taken per day?
 ```{r perday,warn=FALSE}        
 file2<-file[complete.cases(file),]
 library(data.table)
 library(ggplot2)
 dt<-data.table(file2)
 per_day<-dt[, sum(steps), by="date"]
 ggplot(per_day, aes(x=V1)) + geom_histogram()+xlab("steps")
meanval<-mean(per_day$V1)
medval<-median(per_day$V1)
 ```
 
The mean value of total number steps taken per day is `r meanval`.

The median value of total number steps taken per day is `r medval`.
## What is the average daily activity pattern?
 ```{r daily}
 library(data.table)
 dt<-data.table(file2)

 per_step<-dt[, sum(steps)/61, by="interval"] 
 plot(per_step$interval,per_step$V1,type="l",xlab="interval",ylab="Average nubmer    of  steps")
 max_interval<-per_step[order(per_step$V1,decreasing=T),][1]
  ```
  5-minut interval   with maximum average across all the days is `r max_interval`

## Imputing missing values
 ```{r misvalue}
  sumNA<-sapply(file, function(x) sum(is.na(x)))
  allNA<-sumNA[1]+sumNA[2]+sumNA[3]
  allNA
  dtNA<-file[is.na(file),]
  
  new<-merge(dtNA,per_step)
  new$steps<-new$V1
  new$V1<-NULL
  dt<-data.table(file2)
  dt<-rbind(dt,new,use.names=TRUE)
  dt2<-dt
  
  new_per_day<-dt[, sum(steps), by="date"]
  hist(new_per_day$V1,n=61,main = "New histogram of the total numbers of steps ", xlab      ="steps per day")
  newmeanval<-mean(new_per_day$V1) 
  newmedval<-median(new_per_day$V1)
   
 ```
 New mean value of total number steps taken per day is `r newmeanval`.

 New median value of total number steps taken per day is `r newmedval`.

This values differs from previous. Inputing missing values impact is very strong.
## Are there differences in activity patterns between weekdays and weekends?
```{r weekend}
dateDF<- transform(dt2, weekend=as.POSIXlt(date, format='%Y/%m/%d')$wday %in% c(0, 6))
dateDF$dayOfWeek <- "weekday"
dateDF[dateDF$weekend==TRUE,"dayOfWeek"]<-"weekend"

dateDF$dayOfWeek <-as.factor(dateDF$dayOfWeek)
library(lattice)
xyplot(dateDF$steps~dateDF$interval|dateDF$dayOfWeek, type='l',           
   ylab="Number of steps", xlab="Interval")
```